### 2019-03-28 README.Rmd
Edit compendium DOI
This DOI represents all versions, and will always resolve to the latest one.

[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2019). *Compendium of R code and data for "Le cru et le cuit : processus post-dépôt et altérations différentielles des matériaux céramiques"*. Accessed YYYY-MM-DD. Online at <https://doi.org/xxx/xxx>.

>>>>

[![GitHub Release](https://img.shields.io/github/release/nfrerebeau/archeosciences2019.svg)](https://github.com/nfrerebeau/archeosciences2019/releases)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2613512.svg)](https://doi.org/10.5281/zenodo.2613512)

@@

> Frerebeau, N., Ben Amara, A. et Cantin, N. (2019). *Compendium of R code and data for "Le cru et le cuit : processus post-dépôt et altérations différentielles des matériaux céramiques"*. Accessed YYYY-MM-DD. Online at <https://doi.org/10.5281/zenodo.2613512>.
